Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-15 latex/main.tex
Tweak abstract

% NOTE: currently 155 words

Millions of SARS-CoV-2 genome sequences were collected in
response to the COVID-19 pandemic, forming a dataset of unprecedented
depth and richness.
Estimated genealogies are fundamental to
gleaning information from this ocean of data, 
and form the primary input to many downstream analyses.
A basic assumption of methods to infer genealogies from viral 
genetic sequence data is that recombination is negligible and 
the genealogy is a tree.
Recombinant lineages have risen to global prevalance in SARS-CoV-2,
and therefore such single-tree representations are necessarily
incomplete and potentially misleading.
We present sc2ts, a method to infer reticulate genealogies for SARS-CoV-2
that automaticaly detects and incorporates recombination, 
and apply it to 2.48 million genomes.
We show that the inferred genealogy captures a broad range of 
known evolutionary features and provides novel 
insights into the relationships between previously identified
recombinant lineages.
Together, the inference method, inferred genealogy and 
suite of open-source analysis tools, 
represent a powerful resource for future research.

>>>>

% NOTE: currently 160 words

Millions of SARS-CoV-2 genome sequences were collected in
response to the COVID-19 pandemic, forming a dataset of unprecedented
depth and richness.
Estimated genealogies are fundamental to
gleaning information from this ocean of data, 
and form the primary input to many downstream analyses.
A basic assumption of methods to infer genealogies from viral 
genetic sequence data is that recombination is negligible and 
the genealogy is a tree.
Recombinant lineages have risen to global prevalence in SARS-CoV-2,
and therefore such single-tree representations are necessarily
incomplete and potentially misleading.
We present sc2ts, a method to infer reticulate genealogies for SARS-CoV-2
that automatically detects and incorporates recombination 
in real time.  
We use sc2ts to infer a genealogy of 2.48 million genomes,
and show that it captures a broad range of 
known evolutionary features and provides novel 
insights into the relationships between previously identified
recombinant lineages.
Together, the inference method, inferred genealogy and 
suite of open-source analysis tools, 
represent a powerful resource for future research.
